---
title: "Hierarchical Time Series Forecasting"
output: html_notebook
---


Load libraries and data
```{r}
library(forecast)
library(hts)
library(ggplot2)
library(tibble)
library(dplyr)
library(tidyr)
library(tsibble)
library(stringr)
MyData <-read.csv(file="grped3.csv")
data=ts(MyData,frequency=53)
```

Define necessary functions
```{r}
calculate_aggregate_errors<-function(hts_error) {
  
  #If the calculated MAPE is infinite, change it to 100
hts_error[is.infinite(hts_error[4,])]<-100
  #The first value is the average error at the highest level. var1 captures the mean error at the second level,
  #var2 at the third level, and var3 at the lowest level.
newlist<-list(total=hts_error[[4,1]],var1=mean(hts_error[4,2:6]),var2=mean(hts_error[4,7:16]),
              var3=mean(hts_error[4,17:ncol(hts_error)]))
return(newlist)
}

ts2csv <- function(x,j) {
  #function that takes a time series and saves it in CSV format
  fname <- paste0(deparse(substitute(x)),j, ".csv")
  readr::write_csv(tsibble::as_tsibble(x), fname)
}

```

Gridsearch the various forecasting functions and aggregation methods
```{r}
forecasting_methods=c("arima","ets","rw")
aggregation_methods= c("comb", "bu", "mo", "tdgsf", "tdgsa", "tdfp")
ts_period=tsp(data)[3]
#The number of steps ahead to forecast
numahead<-10
#create a list of lists to capture the errors for each forecast
errors_meta=list()
c<-0
#Create hts (hierarchical time series) object
data.hts<-hts(data,characters = c(1,1,2))
for (method in aggregation_methods) {
  for (fmethod in forecasting_methods) {
    
    errors<-list()
    if (identical(fmethod,"ets")) {
      #exponential time series only takes frequency of 1
      data2<-ts(data,frequency=1)
    } else {
      data2<-data
    }
for (j in numahead:ts_period-numahead) {
  x_i<-window(data2)
  train<-window(data2,start=2,end=5+j/ts_period) %>% hts(characters = c(1,1,2))
  fc<-try(forecast(train,method=method,fmethod=fmethod,h=numahead))
  errors[[j]]<-try(accuracy.gts(window(data.hts,start=5+(j-1)/ts_period,end=5+(j+numahead)/ts_period),fc))
  
}
    errors_meta[[c]]<-errors
    c=c+1 
  }
}
```

Calculate and store the forecast using the best performing parameters, ARIMA for forecasting and bottom up for
aggregation technique
```{r}
fmethod="arima"
method="bu"
numahead<-10
mean_errors<-list()
data.hts<-hts(data,characters = c(1,1,2))
js<-seq(from=1,to=43)
ts_period<- tsp(data)[3]
forecasts<-list()
for (j in js) {
  train<-window(data,start=2,end=5+(j-1)/ts_period) %>% hts(characters = c(1,1,2))
  fc<-forecast(train,method=method,fmethod=fmethod,h=numahead)
  #forecasts[[j]]<-fc
  e<-accuracy.gts(window(data.hts,start=5+j/ts_period,end=5+(j+numahead-1)/ts_period),fc)
  l<-calculate_aggregate_errors(e)
  mean_errors[[j]]<-l

  fcts2_<-aggts(fc,levels=3) %>% ts(frequency=1,start=(54-j),end=(54-j+numahead))
  
  ts2csv(fcts2_,j)
}
```

Try using a fourier transform to capture seasonality, similar to Facebook's Prophet time series library in python.
In order to do this, the fourier is introduced as the exogenous (xreg) variable
```{r}
errors_fourier<-list()
for (j in 0:(ts_period-numahead)) {

data_f<-window(data,start=2,end=5+(j-1)/ts_period)

  train<-window(data,start=2,end=5+(j-1)/ts_period) %>% hts(characters = c(1,1,2))
  
future <- matrix(numeric(numahead * ncol(data_f)), ncol = ncol(data_f)) %>%
  ts(frequency = ts_period, start = tsp(data)[2] + 1 / ts_period)

fc <- forecast(train,
  h = numahead, fmethod = "arima",
  seasonal = FALSE,
  xreg = fourier(data_f, K = 11),
  newxreg = fourier(future, K = 11))
e<-accuracy.gts(window(data.hts,start=5+j/ts_period,end=5+(j+numahead-1)/ts_period),fc)
  l<-calculate_aggregate_errors(e)
  errors_fourier[[j]]<-l
}
```


